Sleep Quality Estimation using Accelerometer Data from Thigh-Mounted Devices During in Free Living Conditions

### 2023-02-24 presentation/index.qmd
update README.md

---
title: "Sleep Quality Estimation using Raw Data from Thigh-Mounted Accelerometers during Free Living Conditions"
subtitle: "(working title)"
author: "Esben Lykke, PhD student"
date: "`r format(Sys.Date(), '%d %B, %Y')`"
format:
  revealjs:
    smaller: true
    theme: moon
    slide-number: true
    preview-links: auto
    logo: images/SDU_WHITE_RGB-png.png
    footer: https://github.com/esbenlykke/sleep_study
    css: my_styles.css
    scrollable: true
embed-resources: true
editor_options: 
  chunk_output_type: console
smooth-scroll: true
bibliography: references.bib
---

>>>>

---
title: "Sleep Quality Estimation using Accelerometer Data from Thigh-Mounted Devices During in Free Living Conditions"
subtitle: "(working title)"
author: "Esben Lykke, PhD student"
date: "`r format(Sys.Date(), '%d %B, %Y')`"
format:
  revealjs:
    smaller: true
    theme: moon
    slide-number: true
    preview-links: auto
    logo: images/SDU_WHITE_RGB-png.png
    footer: https://github.com/esbenlykke/sleep_study
    css: my_styles.css
    scrollable: true
embed-resources: true
editor_options: 
  chunk_output_type: console
smooth-scroll: true
bibliography: references.bib
---
